---
title: "Data Prep"
author: "Raphaël Morsomme"
date: "January 16, 2020"
output: pdf_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(fig.height = 4,
                      fig.width = 6,
                      echo = FALSE)

library(tidyverse)
library(GGally) # ggpairs()
library(tidyimpute) # NA imputation
library(na.tools) # NA imputation
library(MASS)
library(rstanarm)
my_standardize <- function(x) (x - mean(x, na.rm = T)) / sd(x, na.rm = T)
```

## Data Preparation

- drop albumin
- remove female with length of gestation superior to 45 weeks and dichotomize the variable
- aggregate scaled PCB's (could do PCA)
- total fat
- exposure (quantity of chemical in environment)

```{r data prep}
d <- readRDS("Longnecker.rds") %>%
  
  mutate_at(vars(center, smoking_status), factor) %>%
  dplyr::select(-albumin) %>% # too many NAs
  
  # Dependent Variable
  filter(gestational_age <= 45) %>% # more accurate treatment would be to allow for error in measurement since the number of weeks is only estimated (there is room for error)
  mutate(outcome_2 = case_when(gestational_age <= 37 ~ "Pre term",
                               TRUE                  ~ "At term"),
         outcome_3 = case_when(gestational_age <= 34 ~ "0Dangerous",
                               gestational_age <= 37 ~ "1Pre term",
                               TRUE                  ~ "2At term")) %>%
  mutate(outcome_3 = outcome_3 %>% factor) %>%
  
  # Aggregate PCBs
  mutate_at(vars(starts_with("pcb")), my_standardize) %>% # standardize pcb's to give them all equal weight in the aggregate pcb variable
  rowwise() %>%
  mutate(pcb = mean(c(pcb_028, pcb_052, pcb_074, pcb_105, pcb_118, pcb_153, pcb_170, pcb_138, pcb_180, pcb_194, pcb_203))) %>%
  ungroup %>%
  
  # Fat
  mutate(fat = 2.27 * cholesterol + triglycerides + 0.623) %>% # https://www.ncbi.nlm.nih.gov/pmc/articles/PMC3893492/
  
  # Exposure
  mutate(dde_env = dde / fat,
         pcb_env = pcb / fat) %>%
  
  # NA
  impute_if(na.mean, is.numeric) %>%
  #impute_if(na.mode, is.character) %>% # not necessary
  
  dplyr::select(starts_with("outcome"), # Y
                starts_with("dde|pcb"), # X
                starts_with("score"), race, maternal_age, center, smoking_status, # Z
                everything())
```

## EDA

- justify aggregation of pcb: they are all correlated, tell the same story, reduce number of predictor (more stable parameter estimation).

```{r, fig_height = 3}
d %>% 
  dplyr::select(dde, pcb, pcb_028 : pcb_203) %>%
  #mutate_all(~(log(. + 0.1))) %>%
  ggcorr(palette = "RdBu", label = TRUE)
```

side-by-side boxplots:
- dde & pcb per outcome_3
- fat per race

side-by-side barplot
- gestation per center
- gestation per race

```{r}
d %>%
  ggplot(aes(x=as.factor(center), fill = outcome_3)) +
  geom_bar(position = "fill")
d %>%
  ggplot(aes(x=as.factor(race), fill = outcome_3)) +
  geom_bar(position = "fill")
```


## Model


The cumulative logistics model is fitted.
```{r}
cumlogit_model_lipid=polr(outcome_3 ~ dde_env + pcb_env + race + maternal_age + score_occupation + center + score_income + score_education, d, 
     contrasts = NULL, Hess = FALSE, model = TRUE,
     method = c("logistic"))
summary(cumlogit_model_lipid)
```
Cumulative Logit model w/o env considering lipid is fitted.
```{r}
###Model 1_
library(MASS)
cumlogit_model=polr(outcome_3 ~ dde + pcb + race + maternal_age + score_occupation + center + score_income + score_education, d, 
     contrasts = NULL, Hess = FALSE, model = TRUE,
     method = c("logistic"))
#summary(cumlogit_model)
exp(-coef(cumlogit_model))
```
-Variable Selection (AIC)
-Model Checking (i) residuals (ii) (probabilistic) predictive model checking
-Try to fit a Bayesian model
-Interpretation
-Try to summarize the result

Bayesian modelling
```{r}
#d_small <- d %>% sample_n(1500)

m <- stan_polr(
  outcome_3 ~ dde_env + pcb_env + race + maternal_age + score_occupation + center + score_income + score_education,
  d,
  iter=3*1e3,
  chains=5,
  method = "logistic", 
  prior = NULL)

m %>% summary
```


