---
title: "Data Prep"
author: "Raphaël Morsomme"
date: "January 16, 2020"
output: pdf_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(fig.height = 4,
                      fig.width = 6,
                      echo = FALSE)
library(tidyverse)
library(GGally) # ggpairs()
library(tidyimpute) # NA imputation
library(na.tools) # NA imputation
library(MASS)
library(sure) # Surrogate Residuals
library(rstanarm)
library(ggpubr)
library(corrplot)
library(mice)
library(RColorBrewer)
library(purrr) # partial()
ggplot2::theme_set(ggplot2::theme_bw())
my_standardize <- function(x) (x - mean(x, na.rm = T)) / sd(x, na.rm = T)

fig_height <- 3.5
fig_width <- 5
fig_path <- "Slides/Rsweave"
legend_size <-  13

my_ggsave <- purrr::partial(ggsave, path = fig_path, width= fig_width, height = fig_height)
```

## Data Preparation

- drop albumin
- remove female with length of gestation superior to 45 weeks and dichotomize the variable
- aggregate scaled PCB's (could do PCA)
- total fat
- exposure (quantity of chemical in environment)

```{r data prep}
d <- readRDS("Longnecker.rds") %>%
  
  mutate_at(vars(center, smoking_status), factor) %>%
  dplyr::select(-albumin) %>% # too many NAs
  
  # Dependent Variable
  filter(gestational_age <= 45) %>% # more accurate treatment would be to allow for error in measurement since the number of weeks is only estimated (there is room for error)
  mutate(outcome_2 = case_when(gestational_age <= 37 ~ "Pre term",
                               TRUE                  ~ "At term"),
         gestgroup = case_when(gestational_age <= 34 ~ "Dangerous",
                               gestational_age <= 37 ~ "Pre term",
                               TRUE                  ~ "At term")) %>%
  mutate(gestgroup = gestgroup %>% factor %>% fct_relevel("Dangerous", "Pre term", "At term")) %>%
  
  # Aggregate PCBs
  mutate_at(vars(starts_with("pcb")), my_standardize) %>% # standardize pcb's to give them all equal weight in the aggregate pcb variable
  rowwise() %>%
  mutate(pcb = mean(c(pcb_028, pcb_052, pcb_074, pcb_105, pcb_118, pcb_153, pcb_170, pcb_138, pcb_180, pcb_194, pcb_203))) %>%
  ungroup %>%
  
  # Fat
  mutate(fat = 2.27 * cholesterol + triglycerides + 0.623) %>% # https://www.ncbi.nlm.nih.gov/pmc/articles/PMC3893492/
  
  # Exposure
  mutate(dde_env_bc = dde / log(fat),
         pcb_env_bc = pcb / log(fat)) %>%
  
  # Race
  mutate(race_agg = case_when(race == "white" ~ "white",
                              TRUE            ~ "non white") ) %>%
  
  # NA
  impute_if(na.mean, is.numeric) %>%
  #impute_if(na.mode, is.character) %>% # not necessary
  
  dplyr::select(starts_with("outcome"), # Y
                starts_with("dde|pcb"), # X
                starts_with("score"), race, maternal_age, center, smoking_status, # Z
                everything())
```

## EDA

- justify aggregation of pcb: they are all correlated, tell the same story, reduce number of predictor (more stable parameter estimation).
- dde & pcb per gestgroup: (i) white less exposed to dde, (ii) "dangerous" has larger value of dde, (iii) no clear relationship for pcb
- fat per race
- gestation per race & per center

```{r, echo=FALSE, fig.align='center', fig.height=3, fig.width=5}
# PCB and gestgroup
pcb_race = ggplot(d) +
  geom_boxplot(aes(x=gestgroup, y=pcb_env_bc, fill=race_agg))+
  ylab("Adjusted PCB")+
  labs(fill="Race")+
  xlab("")+
  facet_grid(~"Adjusted PCB by group")  + theme(legend.text=element_text(size=legend_size))

# DDE and gestgroup
dde_race = ggplot(d) +
  geom_boxplot(aes(x=gestgroup, y=dde_env_bc, fill=race_agg))+
  ylab("Adjusted DDE")+
  labs(fill="Race")+
  xlab("")+
  facet_grid(~"Adjusted DDE by group")  + theme(legend.text=element_text(size=legend_size))

ggarrange(pcb_race, dde_race, ncol=2, 
          common.legend = T, legend = "bottom")

my_ggsave("pcb_dde_per_gest.jpeg")
```

```{r}
jpeg('Slides/Rsweave/pcb_corr.jpeg')
d %>% 
  dplyr::select(starts_with("pcb")) %>%
  cor(use = "pairwise.complete.obs" ) %>%
  corrplot(col=brewer.pal(n=8, name="RdYlBu"))
dev.off()
```

```{r}
d %>%
   ggplot(aes(x=reorder(center, gestgroup == "Dangerous"), fill = gestgroup)) +
   geom_bar(position = "fill") +
   scale_fill_brewer(name = "Outcome", palette = "Spectral") +
   labs(x = "Centers", y = "Count") +
   theme(legend.position = "bottom")  + theme(legend.text=element_text(size=legend_size))

my_ggsave("outcome_per_center.jpeg")
```


## Model

### Model Building
The cumulative logistics model(ordinal regression model) is fitted. The model is paramterized as:
$$
logit(P(Y\leq j))=\beta_{j0}-\eta_1x_1-\cdots-\eta_px_p
$$


The cumulative logistics model is fitted. First, we detect the full model. Then, we make a variable selection.
```{r}
d_subset= d %>% 
  dplyr::select(gestgroup, dde_env,
                pcb_env,race,maternal_age,score_occupation,
                center,score_income,score_education, smoking_status)
cumlogit_model_env_full = polr(gestgroup ~ . + center*dde_env 
                               + center*pcb_env +
                                 race*dde_env +
                                 race*pcb_env, data=d_subset,
                          method = c("logistic"))
summary(cumlogit_model_env_full)
```
without the correction for fat
```{r}
d_subset= d %>% 
  dplyr::select(gestgroup, dde,
                pcb,race,maternal_age,score_occupation,
                center,score_income,score_education)
cumlogit_model_env_full = polr(gestgroup ~ . + center*dde 
                               + center*pcb +
                                 race*dde +
                                 race*pcb, data=d_subset,
                          method = c("logistic"))
summary(cumlogit_model_env_full)
```

```{r}
# Variable selection
cumlogit_model_env_selected=stepAIC(cumlogit_model_env_full,direction="both")
summary(cumlogit_model_env_selected)
res=resids(cumlogit_model_env_selected) #surrogate residuals
autoplot(res, what = "covariate", x =d$pcb_env, xlab = "PCB/Lipids")
autoplot(res, what = "covariate", x =d$dde_env, xlab = "DDE/Lipids")
```
```{r}
# Parameter interpretations
exp(coef(cumlogit_model_env_selected))
```
Interpretation: following the reasoning in the UCLA guide, the odds of of being more likely to have a less dangerous delivery are multiplied by
\begin{itemize}
\item $0.0184957$ if $DDE/Lipid$ increases by 1\% unit
\item $0.00$ if $PCB/Lipid$ increases by 1\% unit
\end{itemize}
\textcolor{red}{this intepretation does not make sense. It should be the opposite}.

```{r}
d_subset= d %>% 
  dplyr::select(gestgroup, dde_env_bc,
                pcb_env_bc,race_agg,maternal_age,score_occupation,
                center,score_income,score_education, smoking_status)
cum_logit_model_bc= polr(gestgroup ~ . + dde_env_bc*race_agg + pcb_env_bc*race_agg + dde_env_bc*center + pcb_env_bc*center, data=d_subset,method = c("logistic"))
cumlogit_model_env_selected=stepAIC(cum_logit_model_bc,direction="both")
summary(cumlogit_model_env_selected)
exp(-coef(cumlogit_model_env_selected))
#summary(cum_logit_model_bc)
#exp(-coef(cum_logit_model_bc))
```
After box-cox transformation & stepwise AIC selection, the final model we choose is "gestgroup ~ dde_env_bc + pcb_env_bc + race_agg + center + smoking_status + dde_env_bc:race_agg + pcb_env_bc:race_agg".
```{r}
res=resids(cum_logit_model_bc) #surrogate residuals
autoplot(res, what = "covariate", x =d$pcb_env_bc, xlab = "PCB/Lipids")
autoplot(res, what = "covariate", x =d$dde_env_bc, xlab = "DDE/Lipids")
autoplot(res, what = "qq", x =d$pcb_env_bc, xlab = "PCB/Lipid")
autoplot(res, what = "qq", x =d$DDE_env_bc, xlab = "DDE/Lipid")
```

```{r}
cumlogit_model_env=polr(
  gestgroup ~ dde_env + pcb_env + race + maternal_age + score_occupation + center + score_income + score_education, 
  d, 
  method = c("logistics"))
summary(cumlogit_model_env)
```


Besides, the cumulative Logit model w/o env is fitted.
=======
Cumulative Logit model w/o env considering lipid is fitted.

```{r}
###Model 1_
library(MASS)
cumlogit_model=polr(gestgroup ~ dde + pcb + race + maternal_age + score_occupation + center + score_income+score_education,             d, 
     method = c("logistic"))
summary(cumlogit_model)
#exp(-coef(cumlogit_model))
```

<<<<<<< HEAD
### Variable Selection
=======
-Variable Selection (AIC)
Stepwise regression by AIC is used to select variables. The final model we choose is "gestgroup ~ dde_env + pcb_env + center + score_education".
```{r}
finalmodel=stepAIC(cumlogit_model_env,direction="both")
```

### Model Diagnostics
- Boxcox transformation of lambda for lipid adjustment
```{r}
# A function to implement box-cox
boxcox_transfomation = function(y, lambda){
  if(lambda==0){
    return(log(y))
  } else {
    return((y^lambda-1)/lambda)
  }
}
# Import the original data
d_boxcox_check= d %>% 
  dplyr::select(gestgroup,race,maternal_age,score_occupation,
                center,score_income,score_education, smoking_status)
# Compute the boxcox
lambda_list = seq(0,2,0.05)
BOXCOX = NULL
for(lambda in lambda_list){
  d_boxcox_check$dde_check = d$dde/boxcox_transfomation(d$fat, lambda)
  d_boxcox_check$pcb_check = d$pcb/boxcox_transfomation(d$fat, lambda)
    model_lambda = polr(gestgroup ~ . + center*dde_check 
                                   + center*pcb_check +
                                     race*dde_check +
                                     race*pcb_check, data=d_boxcox_check,
                              method = c("logistic"))
    log_likelihood = logLik(model_lambda)
    BOXCOX = rbind(BOXCOX, data.frame("lambda"=lambda, "log_likelihood" = log_likelihood))
}
ggplot(BOXCOX)+
  geom_point(aes(x=lambda, y=log_likelihood))
```

-Model Checking (i) residuals 
Surrogate residuals are used to check if the model assumption is correct, as suggested by (Liu and Zhang, 2017). If the model assumptions are correct, then the surrogate residuals $R_S$ will have three properties:
\begin{itemize}
 \item $E(R_S|X)=0$
 \item $Var(R_S|X)=c$, the conditional variance of $R_S$ is constant
 \item The emiprical distribution of $R_S$ resembles an explicit distribution that is related to the link function $G^{-1}(\cdot)$. Specifically, $R_S\sim G(c+\int ud G(u))$.
\end{itemize}

The surrogate residuals vs covariate plot is used to check the first and second properties. The QQ-plot is used to check the third property.

-Residual vs Pcb 
The surrogate residuals are scatter around 0 evenly. This plot indicates that $E(R_S|X)=0$ and $Var(R_S|X)=c$ are basically satisfied.
```{r}
res=resids(finalmodel) #surrogate residuals
autoplot(res, what = "covariate", x =d$pcb, xlab = "pcb")
```

-QQ-plot 
Both the theoretical quantiles and sample quantiles match quite well. Our model assumptions are appropriate.
```{r}
autoplot(res, what = "qq", x =d$dde, xlab = "dde")
```

(ii) (probabilistic) predictive model checking
Will check & compare with other competing models.

### Try to fit a Bayesian model
A Bayesian model is fitted. 5 chains with 3000 iterations each are ran. All Rhats are closed to 1 and effective sample sizes exceed 8000, so there is strong evidence that the chains converge. 
```{r}
m <- stan_polr(
  gestgroup ~ dde_env_bc + pcb_env_bc + race_agg + center + smoking_status + dde_env_bc:race_agg + pcb_env_bc:race_agg,
  d,
  iter=8*1e3,
  chains=1,
  method = "logistic", 
  prior = NULL)
m %>% summary
```
-Printing the 95% credible intervals
```{r}
posterior_interval(m,prob=.95) 
```
-Histrograms of posterior draws for each coefficient are plotted
```{r}
plot(m,"hist")
```
Plot credible intervals:
```{r}
plot(m,"intervals")
```

## Interpretation

The explanation of coefficients are as follows:
If other covariates are held constant, when a covariate $x$ increases by one unit, the cumulative odd ratio $\frac{Pr(Y\leq j)}{1-Pr(Y\leq j)}$ increases by $(exp(-\eta_x)-1)*100\%$. 

Printing
```{r}
-coef(m)
exp(-posterior_interval(m,prob=.95))
```
```{r}
ints=-posterior_interval(m)[c(1,2,16,17),]
means=-coef(m)[c(1,2,16,17)]
resmat=cbind(ints,t(t(means)))
colnames(resmat)=c("95%","5%","mean")
rownames(resmat)=c("adjDDE","adjPCB","adjDDE*white","adjPCB*white")
resmat[,c(1,2,3)] = resmat[,c(3,2,1)]
colnames(resmat) = c("mean", "5%", "95%")
```

## Try to summarize the result
Graphical Summary of the cumulative probability

```{r}
k=30
newdata=m$x[1:k,]
newdata=as.data.frame(newdata)
newdata$dde_env_bc=seq(0,k-1)
newdata$pcb_env_bc=rep(mean(d$pcb_env_bc),k)
newdata$race_aggwhite=rep(1,k) #all whites
newdata$smoking_status1=rep(1,k) #no smoking 
newdata$`dde_env_bc:race_aggwhite`=newdata$dde_env_bc*newdata$race_aggwhite
newdata$`pcb_env_bc:race_aggwhite`=newdata$pcb_env_bc*newdata$race_aggwhite
mu0=as.matrix(newdata) %*% -coef(m)+m$zeta[1] #mu of Pr(Y<=0)
mu1=as.matrix(newdata) %*% -coef(m)+m$zeta[2] #mu of Pr(Y<=1)
prob_cum0=1/(1+exp(-mu0))
prob_cum1=1/(1+exp(-mu1))
prob0=prob_cum0
prob1=prob_cum1-prob_cum0
prob2=1-(prob0+prob1)
#####Calculate CIs
draws=as.matrix(m)
beta=-draws[,1:17]
zeta0=draws[,18]
zeta1=draws[,19]
mu0_draws=as.matrix(newdata) %*% t(beta)+zeta0
mu1_draws=as.matrix(newdata) %*% t(beta)+zeta1
prob_cum0_draws=1/(1+exp(-mu0_draws))
prob_cum1_draws=1/(1+exp(-mu1_draws))
prob0_draws=prob_cum0_draws
prob1_draws=prob_cum1_draws-prob_cum0_draws
prob2_draws=1-prob_cum1_draws
prob0_quants=apply(prob0_draws,1,quantile,prob=c(.05,.95)) ##Calculate the quantiles of P(Y=0)
prob1_quants=apply(prob1_draws,1,quantile,prob=c(.05,.95)) ##Calculate the quantiles of P(Y=1)
prob2_quants=apply(prob2_draws,1,quantile,prob=c(.05,.95))
prob2=1-(prob0+prob1)

```

Plot Pr(Y=j|dde) vs dde
```{r}
predict_DDE_w = tibble(dde = seq(0,k-1),
       p0 = prob0, p1 = prob1, p2=prob2) %>%
  gather(Outcome, Probability,p0,p1,p2) %>%
    mutate(Outcome = case_when(Outcome == "p0" ~ "Dangerous",
                             Outcome == "p1" ~ "Pre term", 
                             TRUE~"At term"))%>%
  mutate(low = c(prob0_quants[1,], prob1_quants[1,],prob2_quants[1,]),
         upp = c(prob0_quants[2,], prob1_quants[2,],prob2_quants[2,])) %>%
  ggplot(aes(x=dde)) +
  geom_line(aes(y=Probability, col = Outcome)) +
  geom_ribbon(aes(ymin = low, ymax = upp, fill = Outcome), alpha = 0.1) +
  theme(legend.position = "bottom")+
  xlab("Adjusted DDE") +
  facet_grid(~"Race = White")  + theme(legend.text=element_text(size=legend_size))
```

Plot Pr(Y=j|pcb) vs pcb
```{r}
k=50
newdata=m$x[1:k,]
newdata=as.data.frame(newdata)
newdata$dde_env_bc=rep(mean(d$dde_env_bc),k)
newdata$pcb_env_bc=seq(-0.3,.8,length.out =k )
newdata$race_aggwhite=rep(1,k) #all whites
newdata$smoking_status1=rep(1,k) #non smoking 
newdata$`dde_env_bc:race_aggwhite`=newdata$dde_env_bc*newdata$race_aggwhite
newdata$`pcb_env_bc:race_aggwhite`=newdata$pcb_env_bc*newdata$race_aggwhite
mu0=as.matrix(newdata) %*% -coef(m)+m$zeta[1] #mu of Pr(Y<=0)
mu1=as.matrix(newdata) %*% -coef(m)+m$zeta[2] #mu of Pr(Y<=1)
prob_cum0=1/(1+exp(-mu0))
prob_cum1=1/(1+exp(-mu1))
prob0=prob_cum0
prob1=prob_cum1-prob_cum0
prob2=1-(prob1+prob0)
#####Calculate CIs
draws=as.matrix(m)
beta=-draws[,1:17]
zeta0=draws[,18]
zeta1=draws[,19]
mu0_draws=as.matrix(newdata) %*% t(beta)+zeta0
mu1_draws=as.matrix(newdata) %*% t(beta)+zeta1
prob_cum0_draws=1/(1+exp(-mu0_draws))
prob_cum1_draws=1/(1+exp(-mu1_draws))
prob0_draws=prob_cum0_draws
prob1_draws=prob_cum1_draws-prob_cum0_draws
prob2_draws=1-prob_cum1_draws
prob0_quants=apply(prob0_draws,1,quantile,prob=c(.05,.95)) ##Calculate the quantiles of P(Y=0)
prob1_quants=apply(prob1_draws,1,quantile,prob=c(.05,.95)) ##Calculate the quantiles of P(Y=1)
prob2_quants=apply(prob2_draws,1,quantile,prob=c(.05,.95)) ##Calculate the quantiles of P(Y=2)


#####Plot
predict_PCB_w = tibble(pcb = seq(-0.3,.8,length.out =k ),
       p0 = prob0, p1 = prob1,p2=prob2) %>%
  gather(Outcome, Probability,p0,p1,p2) %>%
    mutate(Outcome = case_when(Outcome == "p0" ~ "Dangerous",
                             Outcome == "p1" ~ "Pre term", 
                             TRUE~"At term"))%>%
  mutate(low = c(prob0_quants[1,], prob1_quants[1,],prob2_quants[1,]),
         upp = c(prob0_quants[2,], prob1_quants[2,],prob2_quants[2,])) %>%
  ggplot(aes(x=pcb)) +
  geom_line(aes(y=Probability, col = Outcome)) +
  geom_ribbon(aes(ymin = low, ymax = upp, fill = Outcome), alpha = 0.1) +
  theme(legend.position = "bottom")+
  facet_grid(~"Race = White") +
  xlab("Adjusted PCB")  + theme(legend.text=element_text(size=legend_size))

```

For non-white people prob vs dde
```{r}
k=30
newdata=m$x[1:k,]
newdata=as.data.frame(newdata)
newdata$dde_env_bc=seq(0,k-1)
newdata$pcb_env_bc=rep(mean(d$pcb_env_bc),k)
newdata$race_aggwhite=rep(0,k) #all whites
newdata$smoking_status1=rep(1,k) #no smoking 
newdata$`dde_env_bc:race_aggwhite`=newdata$dde_env_bc*newdata$race_aggwhite
newdata$`pcb_env_bc:race_aggwhite`=newdata$pcb_env_bc*newdata$race_aggwhite
mu0=as.matrix(newdata) %*% -coef(m)+m$zeta[1] #mu of Pr(Y<=0)
mu1=as.matrix(newdata) %*% -coef(m)+m$zeta[2] #mu of Pr(Y<=1)
prob_cum0=1/(1+exp(-mu0))
prob_cum1=1/(1+exp(-mu1))
prob0=prob_cum0
prob1=prob_cum1-prob_cum0
prob2=1-(prob0+prob1)
#####Calculate CIs
draws=as.matrix(m)
beta=-draws[,1:17]
zeta0=draws[,18]
zeta1=draws[,19]
mu0_draws=as.matrix(newdata) %*% t(beta)+zeta0
mu1_draws=as.matrix(newdata) %*% t(beta)+zeta1
prob_cum0_draws=1/(1+exp(-mu0_draws))
prob_cum1_draws=1/(1+exp(-mu1_draws))
prob0_draws=prob_cum0_draws
prob1_draws=prob_cum1_draws-prob_cum0_draws
prob2_draws=1-prob_cum1_draws
prob0_quants=apply(prob0_draws,1,quantile,prob=c(.05,.95)) ##Calculate the quantiles of P(Y=0)
prob1_quants=apply(prob1_draws,1,quantile,prob=c(.05,.95)) ##Calculate the quantiles of P(Y=1)
prob2_quants=apply(prob2_draws,1,quantile,prob=c(.05,.95))
prob2=1-(prob0+prob1)
#####plot
predict_DDE_nw = tibble(dde = seq(0,k-1),
       p0 = prob0, p1 = prob1, p2=prob2) %>%
  gather(Outcome, Probability,p0,p1,p2) %>%
    mutate(Outcome = case_when(Outcome == "p0" ~ "Dangerous",
                             Outcome == "p1" ~ "Pre term", 
                             TRUE~"At term"))%>%
  mutate(low = c(prob0_quants[1,], prob1_quants[1,],prob2_quants[1,]),
         upp = c(prob0_quants[2,], prob1_quants[2,],prob2_quants[2,])) %>%
  ggplot(aes(x=dde)) +
  geom_line(aes(y=Probability, col = Outcome)) +
  geom_ribbon(aes(ymin = low, ymax = upp, fill = Outcome), alpha = 0.1) +
  theme(legend.position = "bottom")+
  xlab("Adjusted DDE") +
  facet_grid(~"Race = Non-white")  + theme(legend.text=element_text(size=legend_size))
```
For non-white prob vs pcb
```{r}
k=50
newdata=m$x[1:k,]
newdata=as.data.frame(newdata)
newdata$dde_env_bc=rep(mean(d$dde_env_bc),k)
newdata$pcb_env_bc=seq(-0.3,.8,length.out =k )
newdata$race_aggwhite=rep(0,k) #all whites
newdata$smoking_status1=rep(1,k) #non smoking 
newdata$`dde_env_bc:race_aggwhite`=newdata$dde_env_bc*newdata$race_aggwhite
newdata$`pcb_env_bc:race_aggwhite`=newdata$pcb_env_bc*newdata$race_aggwhite
mu0=as.matrix(newdata) %*% -coef(m)+m$zeta[1] #mu of Pr(Y<=0)
mu1=as.matrix(newdata) %*% -coef(m)+m$zeta[2] #mu of Pr(Y<=1)
prob_cum0=1/(1+exp(-mu0))
prob_cum1=1/(1+exp(-mu1))
prob0=prob_cum0
prob1=prob_cum1-prob_cum0
prob2=1-(prob1+prob0)
#####Calculate CIs
draws=as.matrix(m)
beta=-draws[,1:17]
zeta0=draws[,18]
zeta1=draws[,19]
mu0_draws=as.matrix(newdata) %*% t(beta)+zeta0
mu1_draws=as.matrix(newdata) %*% t(beta)+zeta1
prob_cum0_draws=1/(1+exp(-mu0_draws))
prob_cum1_draws=1/(1+exp(-mu1_draws))
prob0_draws=prob_cum0_draws
prob1_draws=prob_cum1_draws-prob_cum0_draws
prob2_draws=1-prob_cum1_draws
prob0_quants=apply(prob0_draws,1,quantile,prob=c(.05,.95)) ##Calculate the quantiles of P(Y=0)
prob1_quants=apply(prob1_draws,1,quantile,prob=c(.05,.95)) ##Calculate the quantiles of P(Y=1)
prob2_quants=apply(prob2_draws,1,quantile,prob=c(.05,.95)) ##Calculate the quantiles of P(Y=2)


#####Plot
predict_PCB_nw = tibble(pcb = seq(-0.3,.8,length.out =k ),
       p0 = prob0, p1 = prob1,p2=prob2) %>%
  gather(Outcome, Probability,p0,p1,p2) %>%
  mutate(Outcome = case_when(Outcome == "p0" ~ "Dangerous",
                             Outcome == "p1" ~ "Pre term", 
                             TRUE~"At term"))%>%
  mutate(low = c(prob0_quants[1,], prob1_quants[1,],prob2_quants[1,]),
         upp = c(prob0_quants[2,], prob1_quants[2,],prob2_quants[2,])) %>%
  ggplot(aes(x=pcb)) +
  geom_line(aes(y=Probability, col = Outcome)) +
  geom_ribbon(aes(ymin = low, ymax = upp, fill = Outcome), alpha = 0.1) +
  theme(legend.position = "bottom")+
  facet_grid(~"Race = Non-white")+
  xlab("Adjusted PCB") + theme(legend.text=element_text(size=legend_size))
```
Last Plot
```{r}
ggarrange(predict_DDE_w, predict_PCB_w, predict_DDE_nw, predict_PCB_nw, 
          nrow =2, ncol=2,common.legend = TRUE , legend = "bottom")

my_ggsave("results.jpeg")
```

##Sensitvity analysis
Varying the prior. Use the prior on R^2 with location=.3, .5, .8
```{r}
m_r2_05 <- stan_polr(
  gestgroup ~ dde_env_bc + pcb_env_bc + race_agg + center + smoking_status + dde_env_bc:race_agg + pcb_env_bc:race_agg,
  d,
  iter=8*1e3,
  chains=1,
  method = "logistic", 
  prior = R2(.5))

m_r2_03 <- stan_polr(
  gestgroup ~ dde_env_bc + pcb_env_bc + race_agg + center + smoking_status + dde_env_bc:race_agg + pcb_env_bc:race_agg,
  d,
  iter=8*1e3,
  chains=1,
  method = "logistic", 
  prior = R2(.3))

m_r2_08 <- stan_polr(
  gestgroup ~ dde_env_bc + pcb_env_bc + race_agg + center + smoking_status + dde_env_bc:race_agg + pcb_env_bc:race_agg,
  d,
  iter=8*1e3,
  chains=1,
  method = "logistic", 
  prior = R2(.8))
```
Look at the credible intervals for .3
```{r}
posterior_interval(m_r2_03)
```
for .5
```{r}
posterior_interval(m_r2_05)
```
for .8
```{r}
posterior_interval(m_r2_08)
```
Our method is not sensitive to priors.




